### 2021-09-15 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\uline{
$A_{paste}$ means that, in the region where the perturbation is pasted, the pixel values of the original image is replaced with the pixel values of the perturbation.
% 解释加法
The operator $A_{add}$ means to apply additive noise, where the injecting small perturbations into the input samples. Often need constraint. the injected noise are small and sometimes invisible.  
}

%%%% 问题 2.2 %%%%
\textit{2. I agree with reviewer 3, the ground truth boxes are inaccessible to trackers during the inference. It seems that the authors use the ground truth boxes to generate the fake trajectory in lines 51-57 on page 7. Please clarify it.}

\textbf{We generate new trajectory without the test GT: we let the fake box run straight to border of the image, speed and derection is random. For your convenience in cross-checking, the new text is given as follows.}

\uline{\textit{Ablation Study: An alternative way to generate the fake trajectory}  Here, we consider an alternative way to generate the \textit{fake trajectory}. Specifically, the attacker forces the tracker to follow a fixed direction. We illustrate this with 4 different directions, consisting of shifting the box by $(\pm 3, \pm 3)$ pixels in each consecutive frames, corresponding to the four directions $45^{\circ}, -45^{\circ}, 135^{\circ}, -135^{\circ}$.}

@@

\begin{table}[t]
  \centering
  \caption{Influence of different ways to generate the fake trajectory. One way is the fake trajectory to follow a fixed direction. The other way is the fake trajectory to follow the real target. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{Type of the Fake Trajectory} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{2-5}
                              & AO                & SR                & AO               & SR               \\ \midrule
  Fixed direction             & 0.175             & 0.144             & 0.845            & 0.897            \\
  Follow the real target      & 0.153             & 0.123             & 0.840            & 0.890            \\ \bottomrule        
  \end{tabular}
  \label{table:direction}
\end{table}

%%%% 问题 2.3 %%%%
\textit{3. For the experiments, the authors should conduct the ablation study on only adding perturbations on the template images or the search regions to show the impact of $p$ and $\delta$.}

\textbf{Thanks for your advice and we have conducted the ablation study on only adding perturbations on the template images or the search regions to show the impact of $p$ and $\delta$. As we can see, only use one of them is not useful, because they are trained together. For your convenience of cross review, the new text is given as follows.}

\uline{\textit{One Branch Attack} To see the impact of $p$ and $\delta$, we add the ablation study on only adding perturbations on the template images or the search regions. The result is shown in table \ref{table:one_branch}. Experiment results shows that only adding the perturbation to one branch is not useful.
% 对比无目标攻击性能。
For the untargeted attack, only attacking the template/search branch leads to the AO of 0.510/0.714, while attacking both branches leads to the AO of 0.153, which is more effective.
% 有目标
For the targeted attack, only attacking the templat/search branch leads to the AO of 0.156/0.160, while attacking both branches leads to the AO of 0.840. Experimental results show that attacking two branches can achieve better results than attacking one branch.}
